\vspace{-15mm} \Large \textbf{Utilisation of Computer Algorithms in the Optimisation of Building Envelopes Thermal Performance}

### 2013-11-29 Paper.tex
Fri 12:17

Although the process seems to be up till this point relatively simple; it is only theoratically so. Now that the thermal variables which would enable us to control the thermal performance are defined, the method of modelling them into a mathematical function which can be easily input into the optimisation algorithm

>>>>

Now that the thermal variables which would enable us to control the thermal performance are defined, and the theoritcal method of modelling them into a mathematical function illustrated; a practical way of measuring and optimising the thermal performance of the building envelope is the next step.
